\documentclass[11pt]{exam}

\usepackage{listings}
\usepackage{graphicx}
\usepackage{color}


\lstdefinestyle{latexsty}{
	language={[LaTeX]TeX},
    basicstyle=\small\ttfamily,
    breaklines=true,
    breakindent=0pt, 
    numbers=left, stepnumber=1, numbersep=5pt,
    commentstyle=\color{red},
    showstringspaces=false,
    keywordstyle=\color{blue}\bfseries,
    morekeywords={align,begin},
    tabsize=2,
    frame=single,
}

\pagestyle{headandfoot}
\runningheader{\LaTeX: An Introduction (Part 1)}{Exercise 4}{10th February 2014}
\runningheadrule
\runningfooter{}{\thepage}{}
\runningfootrule

\title{Exercise 4 - Including Graphics}
\author{UGC `\LaTeX: An Introduction (Part 1)' Training Course}
\date{February 10th 2014}


\begin{document}
\maketitle

\fbox{\parbox{0.9\textwidth}{In this exercise, we will start to include graphics in our \LaTeX\ documents.}}

\vspace{0.2in}

\begin{questions}

\question
If it's not already open, open TeXworks. Either create a new file for this exercise and save it somewhere appropriate, or open an existing file.
\question
Find a picture somewhere that you would like to include in your document. Google image search is a good place to start looking.
\question
Save the picture in the same folder as your \LaTeX\ document.
\question
Add the \texttt{graphicx} package to your document and use the \texttt{{\textbackslash}includegraphics} command to include the image you just saved in your document.
\question
Repeat the process and add another image to your document
\question
Experiment with the different image sizing, scaling, cropping and rotating options. Can you scale an image up and down? Can you set an image to be a quarter of the width of your document? When you rotate an image, does it rotate clockwise or anti-clockwise? Can you trim the edges of an image so they do not appear?
\question
Experiment with placing boxes around your images. Change the distance between the image and the border, and the thickness of the border.
\end{questions}

\end{document}